Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-01-10 papers/02 journal v2/journal_v14.tex

\smallskip
We consider a linear approximation of power-flow equations, which is standard in the literature of P2P markets, e.g., \cite{yang2019,moret2020}. Specifically, for each bus $y \in \mc B$, it must hold that
\begin{equation}
\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \eta_i - p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
\end{equation}
where $\eta_i$ is the local power unbalance of prosumer $i$, i.e.,
\begin{equation}
\label{eq:etai}
\eta_i := p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}.
\end{equation}
Equation \eqref{eq:p_bal_p} represents the local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers. Moreover, it must hold that
\begin{subequations}
\small
\label{eq:pf_pq}
\begin{align}
&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \, \, \forall z \in \mc B_y, \label{eq:pf_p}\\
&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \, \,  \forall z \in \mc B_y, \label{eq:pf_q}
\end{align}
\label{eq:pf_all}
\end{subequations}
which represent the power flow equations of line $(y,z)$ from the perspective of bus $y$, with $B_{(y,z)}$ and  $G_{(y,z)}$ denoting the susceptance and conductance, respectively, of line $(y,z)$. Note that by \eqref{eq:pf_p} and \eqref{eq:pf_q}, for each pair $(y,z) \in \mc L$, it holds that $p_{(y,z)}^{\ell} = {-p}_{(z,y)}^{\ell}$ and $q_{(y,z)}^{\ell} = {-q}_{(z,y)}^{\ell}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Semi-decentralized Coordinated Market Clearing}
Several semi-decentralized and distributed algorithms have been recently proposed to find a solution of the generalized aggregative game in \eqref{eq:locOpt}, e.g. \cite{paccagnan2019,belgioioso2020semi,belgioioso2020b,
gadjov2020single,bianchi2020fast}. 
%
\marginnote{\note{R1-5}\\ \note{R2-6}\\ \note{R3-4}}
\edit{%
Among these methods, we focus on semi-decentralized ones \cite{belgioioso2020semi}, in which the agents (i.e., prosumers) rely on a reliable central coordinator (i.e., the DNO) that gathers local variables in aggregative form and then broadcasts (incentive) signals for coordination purposes. % and general in terms of convergence guarantees.

%
In this paper, we exploit the special linear coupling structure in the cost functions \eqref{eq:cost_def} and coupling constraints \eqref{eq:Cconstr_def} to tailor Algorithm~6 in \cite{belgioioso2020semi} for our P2P market game.
%
Unlike most of the available semi-decentralized pseudo-gradient-based methods, \cite[Algorithm~6]{belgioioso2020semi} relies on proximal updates that are computationally more expensive but greatly mitigate the overall communication burden between agents and coordinator.

%
The resulting market-clearing mechanism, summarized in Algorithms~1, requires the prosumers and the DNO to store, update, and communicate some additional (dual and auxiliary) variables, whose primary function is to coordinate the system towards operational feasibility and trading reciprocity. In particular, each prosumer $i\in\mc N$ stores in its local memory
\begin{itemize}
\item the local strategy $u_i$ that collects the power generation, storage (charging/discharging), load, and trading profiles.

@@

\text{Step sizes}: set $
 \alpha_i \!<\! 
({3} +N \max_{h}\, d_h^{\text{mg}})^{-1}$, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$.

@@

\medskip
\noindent
(ii) \text{Primal update (generation, storage, load, and trading):}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
\psi_i(k) = u_i(k)-
	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
	\hspace*{5em}
	{
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\[1em]
%
\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.3em]
\left\{
\begin{array}{r l}
	\underset{\xi \in \R^{n_i}}{\argmin} & 
	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \!-\! p_i^{\text{mg}}(k) \!+\! \xi \big) 
	+ \frac{1}{2 \alpha_i}
	\left\| \xi -  \psi_i(k) 
	\textstyle
	  \right\|^2 \\
	\text{s.t.} & \xi \in \mc U_i
\end{array} 
\right.
\end{array}
\right.
$

@@

\medskip
\noindent 
(i) \text{Primal update (network physical variables):}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%\text{Receive } \\
\psi(k) \!=\!\col \Big( 
	\left\{
	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B} \Big)\\[.7em]
%
u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
\end{array}
\right.
$

\medskip
\noindent
\noindent 
(ii) \text{Dual update (operational feasibility):}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%
\eta(k\!+\!1) = 
	\left[
	\begin{smallmatrix}
	1\\
	- 1 
	\end{smallmatrix}
	\right] \otimes (2 \sigma^{\text{mg}}(k\!+\!1)- \sigma^{\text{mg}}(k)) 
	-
	\left[
	\begin{smallmatrix}
	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
	\end{smallmatrix} 
	\right]\\
	% lambda update
	\lambda^{\text{mg}}(k+1) = \textstyle
	\proj_{\R^{2 H}_{\geq 0}}\left( 
	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
	 \right)\\
%
\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
	(k\!+\!1)+b- \sigma^{\text{tg}}(k\!+\!1)\\
	%
	\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))\\[.5em]
	%
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
\left|
\begin{array}{l}
%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
\hspace*{9em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
%
\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k\!+\!1)- \zeta^{\text{pb}}_y(k))
\end{array}
\right.
\end{array}
\right.
$

@@

\item The primal update of each prosumer (Algorithm~2~(ii)) involves the solution of a quadratic program\footnote{Up to a fairly-standard reformulation of the absolute value term in \eqref{eq:f_t}.}, for which very efficient solvers are available, e.g. \cite{osqp}. \edit{In there, if $ \tilde  J_{i} \big( \xi, \sigma^{\text{mg}}(k) \!-\! p_i^{\text{mg}}(k) \!+\! \xi \big)$ is replaced by its approximate version $ \tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big)$, obtained by neglecting prosumer $i$'s contribution $p_i^{\text{tr}}$ to the aggregative active load $\sigma^{\text{mg}}$, Algorithm 1 will converge to a variational Wardrop equilibrium \cite[\S~II.B]{belgioioso2020semi}, which is a good approximation of v-GNEs for networks with a large number of prosumers.}

@@

Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$. The parameter $c_{(i,j)}^{\mathrm{tr}}$ is set larger than $c_i^{\mathrm{di}}$ to encourage trading between prosumers with and without dispatchable units, but is smaller than the average unit-price of importing power from the main grid. Note that, in some simulations, we vary these cost parameters. 
%
%
\subsection{Achieving operationally-safe solutions}
In the first simulation study, we compare the solutions obtained from solving a P2P market model with and without capacity constraints \eqref{eq:line_cap}. We specifically create an extreme case with $25$ prosumers, where the load of  prosumer $10$ (see Figure \ref{fig:simD_safe}) is very high. We solve both market designs using Algorithm \ref{alg:alg1}. Figure \ref{fig:simD_safe} shows the resulting power-line saturations between busses for both designs. 
%
Some equilibrium solutions of the P2P market cause overcapacity in some lines when capacity constraints \eqref{eq:line_cap} are not taken into account in the model, as illustrated in Figure \ref{fig:simD_safe}~(b).

@@

\subsection{The impact of storage units}
In this set of simulations, we investigate the advantages of distributed storage in the network. We generate a test case of 50-prosumer network and consider two extreme scenarios: (a) no prosumers own storage units and  (b) all prosumers own storage units. Furthermore, we also allow some of the prosumers to own distributed generation units. Figures \ref{fig:sim_B1}-\ref{fig:sim_B2} summarize the simulation results. From Figure \ref{fig:sim_B1}, we can see how the storage units help in shaving the peak of total power imported from the main grid and locally generated by distributed generators.

Interestingly, the trading between prosumers is also affected, as shown by the top plot of Figure \ref{fig:sim_B2}. From this plot, we observe that the existence of storage units reduce the total power traded during the peak hours as the prosumers have reserved energy in their storages.
%
Note that the prosumers charge their storage units during the first off-peak hours by buying energy from the main grid and/or from other prosumers that own dispatchable generation units (see the first six hours of the bottom plot of Figures \ref{fig:sim_B1} and those of the top plot of Figure \ref{fig:sim_B2}). 
%
Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows the cost difference between both scenarios. There, we observe that most of the prosumers gain economical benefits by owning a storage unit. The ones that have positive cost differences are those that also own dispatchable generation units.
They gain more profit in scenario (a) since the prosumers that do not own any active components prefer to buy energy from their trading partners that own dispatchable generation units than importing from the main grid. This preference becomes less attractive when these buying prosumers own a storage unit.
%

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v2}
	\caption{Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
	\label{fig:sim_B1}
\end{figure}
\begin{figure}[t]
	%\centering 
	%\hspace{-17pt}
	\includegraphics[width=1\linewidth]{figures/c2a}
	\caption{Aggregated P2P trading (top plot), and individual cost difference (bottom plot), in scenarios (a) and (b).
	}
	\label{fig:sim_B2}
\end{figure}

@@

\subsection{Scalability of the algorithm}
Finally, we perform a scalability test for the proposed algorithm. Specifically, we evaluate the convergence speed, in terms of the total number of iterations required to meet a predetermined stopping criterion, when the size of the population of prosumers $N$ and the connectivity of the trading network (the number of trading links) grow. We carry out two sets of simulations.
%
For the former, we consider five different values of $N$ and a fixed connectivity level of $0.6$ and we run ten Monte Carlo simulations for each $N$, whereas in the latter, the connectivity of the trading network of $50$ prosumers varies in the range $[0.1,1]$, where connectivity $1$ means that the trading network is a complete graph. Similarly, we also run ten Monte Carlo simulations for each connectivity value, see
Figure~\ref{fig:simE}. We can see that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network. These results highlight that our algorithm is suitable to be applied to  large-scale systems.

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simEF1.eps}
	\caption{Total number of iterations for convergence of Alg. 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom). 
	}
	\label{fig:simE}
\end{figure}

@@

\include{appendix}

>>>>

\smallskip
We consider a linear approximation of power-flow equations, which is standard in the literature of P2P markets, e.g., \cite{yang2019,moret2020}. Specifically, for each bus $y \in \mc B$, it must hold that
\begin{equation}
\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \eta_i-p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
\end{equation}
where $\eta_i$ is the real power injection of prosumer $i$, i.e.,
\begin{equation}\label{eq:etai}
\eta_i:= p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}
\end{equation}
Equation \eqref{eq:p_bal_p} models the local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption, and line powers. Moreover, it must hold that
\begin{subequations}
\small
\label{eq:pf_pq}
\begin{align}
&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \, \, \forall z \in \mc B_y, \label{eq:pf_p}\\
&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \, \,  \forall z \in \mc B_y, \label{eq:pf_q}
\end{align}
\label{eq:pf_all}
\end{subequations}
which represent the power flow equations of line $(y,z)$ from the perspective of bus $y$, with $B_{(y,z)}$ and  $G_{(y,z)}$ denoting the susceptance and conductance, respectively, of line $(y,z)$. Note that by \eqref{eq:pf_p} and \eqref{eq:pf_q}, for each pair $(y,z) \in \mc L$, it holds that $p_{(y,z)}^{\ell} = {-p}_{(z,y)}^{\ell}$ and $q_{(y,z)}^{\ell} = {-q}_{(z,y)}^{\ell}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Semi-decentralized Coordinated Market Clearing}
Several semi-decentralized and distributed algorithms have been recently proposed to find a solution of the generalized aggregative game in \eqref{eq:locOpt}, e.g. \cite{paccagnan2019,belgioioso2020semi,belgioioso2020b,
gadjov2020single,bianchi2020fast}. 
%
\marginnote{\note{R1-5}\\ \note{R2-6}\\ \note{R3-4}}
\edit{%
Among these methods, we focus on semi-decentralized ones \cite{belgioioso2020semi}, in which the agents (i.e., prosumers) rely on a reliable central coordinator (i.e., the DNO) that gathers local variables in aggregative form and then broadcasts (incentive) signals for coordination purposes.

%
In this paper, we exploit the special linear coupling structure in the cost functions \eqref{eq:cost_def} and coupling constraints \eqref{eq:Cconstr_def} to tailor Algorithm~6 in \cite{belgioioso2020semi} for our P2P market game.
%
Unlike most of the available semi-decentralized pseudo-gradient-based methods, \cite[Algorithm~6]{belgioioso2020semi} relies on proximal updates that are computationally more expensive but greatly mitigate the overall communication burden between agents and coordinator.
%
The resulting market-clearing mechanism, summarized in Algorithm~1, requires the prosumers and the DNO to store, update, and communicate some additional (dual and auxiliary) variables, whose primary function is to coordinate the system towards operational feasibility and trading reciprocity. In particular, each prosumer $i\in\mc N$ stores in its local memory
\begin{itemize}
\item the local strategy $u_i$ that collects the power generation, storage (charging/discharging), load, and trading profiles.

@@

@@

\medskip
\noindent
(ii) \text{Primal update (generation, storage, load, and trading):}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
\psi_i(k) = u_i(k)-
	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
	\hspace*{5em}
	{
	%\left(
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 
	%\otimes I_H
%\right)	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\
%
\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.2em]	
\left\{
\begin{array}{r l}
	\underset{\xi \in \R^{n_i}}{\argmin} & 
	 J_{i} \big( \xi, u_{-i}(k) \big) 
	+ \frac{1}{2 \alpha_i}
	\left\| \xi -  \psi_i(k) 
	\textstyle
	  \right\|^2 \\
	\text{s.t.} & \xi \in \mc U_i
\end{array} 
	\right.
\end{array}	
\right.		$

@@

\medskip
\noindent 
(i) \text{Primal update (network physical variables):}\\[.2em]
\hspace*{.15em}
$\left|
\begin{array}{l}
\psi(k) = \col \left( 
	\left\{
	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B} \right)\\[.7em]
%
u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
\end{array}
\right.
$

\medskip
\noindent
\noindent 
(ii) \text{Dual update (operational feasibility):}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%
\eta(k\!+\!1) = 
	\left[
	\begin{smallmatrix}
	1\\
	- 1 
	\end{smallmatrix}
	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
	-
	\left[
	\begin{smallmatrix}
	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
	\end{smallmatrix} 
	\right]\\
	%
	\lambda^{\text{mg}}(k+1) = \textstyle
	\proj_{\R^{2 H}_{\geq 0}}\left( 
	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
	 \right)\\
%
\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
	(k\!+\!1)+b- \sigma^{\text{tg}}(k\!+\!1)\\
	%
	\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))\\[.5em]
	%
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
\left|
\begin{array}{l}
%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
\hspace*{9em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
%
\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k\!+\!1)- \zeta^{\text{pb}}_y(k))
\end{array}
\right.
\end{array}
\right.
$

@@

\item The primal update of each prosumer (Algorithm~2~(ii)) involves the solution of a quadratic program\footnote{Up to a fairly-standard reformulation of the absolute value term in \eqref{eq:f_t}.}, for which very efficient solvers are available, e.g. \cite{osqp}. \edit{In there, if $   J_{i} \big( \xi, u_{-i}(k) \big)$ is replaced by its approximate version $ \tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big)$, obtained by neglecting prosumer $i$'s contribution $p_i^{\text{tr}}$ to the aggregative active load $\sigma^{\text{mg}}$, Algorithm 1 will converge to a variational Wardrop equilibrium \cite[\S~II.B]{belgioioso2020semi}, which is a good approximation of v-GNEs for networks with a large number of prosumers.}

@@

\red{[change cost parameters according to new simulations]} Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$. The parameter $c_{(i,j)}^{\mathrm{tr}}$ is set larger than $c_i^{\mathrm{di}}$ to encourage trading between prosumers with and without dispatchable units, but is smaller than the average unit-price of importing power from the main grid. Note that, in some simulations, we vary these cost parameters. 
%
%
\subsection{Achieving operationally-safe solutions}
In the first simulation study, we compare the solutions obtained from solving a P2P market model with and without capacity constraints \eqref{eq:line_cap}. We specifically create an extreme case with $25$ prosumers, where the load of  prosumer $10$ (see Figure \ref{fig:simD_safe}) is very high. We solve both market designs using Algorithm \ref{alg:alg1}. Figure \ref{fig:simD_safe} shows the resulting power-line saturations between busses for both designs. 
%
Some equilibrium solutions of the P2P market cause overcapacity in some lines when capacity constraints \eqref{eq:line_cap} are not taken into account in the model, as illustrated in Figure \ref{fig:simD_safe}~(b).

@@

\subsection{The impact of storage units}
In this set of simulations, we investigate the advantages of distributed storage in the network. We generate a test case of 50-prosumer network and consider two extreme scenarios: (a) no prosumers own storage units and  (b) all prosumers own storage units. Furthermore, we also allow some of the prosumers to own distributed generation units. Figures \ref{fig:sim_B1}-\ref{fig:sim_B2} summarize the simulation results. From Figure \ref{fig:sim_B1}, we can see how the storage units help in shaving the peak of total power imported from the main grid and locally generated by distributed generators. Interestingly, the trading between prosumers is also affected, as shown by Figure \ref{fig:sim_B2}. From this plot, we observe that the existence of storage units reduce the total power traded during the peak hours as the prosumers have reserved energy in their storages.
%
Note that the prosumers charge their storage units during the first off-peak hours by buying energy from the main grid and/or from other prosumers that own dispatchable generation units (see the first six hours of the bottom plot of Figures \ref{fig:sim_B1} and those of the top plot of Figure \ref{fig:sim_B2}). \edit{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
%
%Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows the cost difference between both scenarios. There, we observe that most of the prosumers gain economical benefits by owning a storage unit. The ones that have positive cost differences are those that also own dispatchable generation units.
%They gain more profit in scenario (a) since the prosumers that do not own any active components prefer to buy energy from their trading partners that own dispatchable generation units than importing from the main grid. This preference becomes less attractive when these buying prosumers own a storage unit.
%

\begin{figure}[t]
	\centering\marginnote{\note{R3-6}} 
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3}
	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
	\label{fig:sim_B1}
\end{figure}
\begin{figure}[t]
	%\centering 
	%\hspace{-17pt}
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v5}
	\caption{Aggregated P2P trading (top plot), and comparison of trading price with grid prices in both scenarios (bottom plot), 
		in scenarios (a) and (b).
	}
	\label{fig:sim_B2}
\end{figure}

@@

\subsection{Scalability of the algorithm}
Finally, we perform a scalability test for the proposed algorithm. Specifically, we evaluate the convergence speed, in terms of the total number of iterations required to meet a predetermined stopping criterion, when the size of the population of prosumers $N$ and the connectivity of the trading network (the number of trading links) grow. We carry out two sets of simulations.
%
For the former, we consider five different values of $N$ and a fixed connectivity level of $0.6$ and we run ten Monte Carlo simulations for each $N$, whereas in the latter, the connectivity of the trading network of $50$ prosumers varies in the range $[0.1,1]$, where connectivity $1$ means that the trading network is a complete graph. Similarly, we also run ten Monte Carlo simulations for each connectivity value, see
\edit{Figures~\ref{fig:simE1}--\ref{fig:simE2}.} We can see that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network. These results highlight that our algorithm is suitable to be applied to  large-scale systems.

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simAg_810.eps}
	\caption{\edit{The total number of iterations (top) and the total computational time per agent in seconds (bottom). }
	}
	\label{fig:simE1}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simCon.eps}
	\caption{\edit{The total number of iterations  vs the connectivity level (the number of trading links). }
	}
	\label{fig:simE2}
\end{figure}

@@

\input{appendix}
